EDIpack2: interoperable Lanczos-based exact diagonalization solver for generic quantum impurity problems.

### 2025-03-21 edipack2.tex
Updated draft. Structure sketched

\section{Structure}\label{SecStruct}
\subsection{EDIpack2}
\subsection{EDIpack2ineq}
\subsection{EDIpack2 C-bindings}
\subsection{EDIpack2Triqs}

@@

\section{Implementation}\label{SecEDIpack}

@@

\subsection{Dynamical correlation functions}

\subsection{Observables}

\subsection{Reduced impurity density matrix}

\subsection{Bath parametrization}

\subsection{Bath Optimization}

\subsection{Input/Output}

@@

@@

>>>>

% ##################################################################
% ##################################################################
% ##################################################################

\section{Structure and derived software}\label{SecStruct}
\NAME is a modular library which contains three principal structures.
At the core is the exact diagonalization solver: \NAME.
Next there is a {\tt EDIpack2ineq} which extends application to the case of multiple
inequivalent impurity problems. Finally, there we provide a Fortran-C
interface, which enables development of additional API or
inter-operability with external libraries.

\begin{itemize}
\item{\bf EDIpack2.}
This constitutes the  building block of the whole software. This part
implement the  with the Lanczos-based solver for generic quantum
impurity systems encoding different symmetries, i.e. quantum number
conservations and apt to solve multi-orbital problems, also in
presence of coupling to local phonons.  
The \NAME solver has a hierarchical and modular structure: different
sections of the library communicate through a shared memory layer. The
top module of the library is {\tt EDIPACK2} which, once loaded,
enables access to the Fortran API in terms of suitable procedures to
initialize, execute and finalize the solver or to retrieve internal
quantities while making opaque to the user the internal structure of
the library. 
A detailed presentation of the library can be found in
Sec.\ref{SecEDIpack}.

\item{\bf EDIpack2ineq.}
This part of the software, leveraging on the object oriented concepts
available in modern Fortran, aims to extend the \NAME library to the
case of multiple inequivalent and independent impurity problems. This
is particularly useful while using \NAME as a solver for DMFT in
presence of unit cells with inequivalent atoms, for systems with
somehow broken translational symmetry (e.g. heterostructures, large
supercells, etc.).

\item{\bf EDIpack2 C-bindings.}
\NAME includes a single module implementing a Fortran-C interface of the main
library procedures. The module is developed around the implicit {\tt
  ISO\_C\_BINDING} capabilities of the most recent Fortran
distributions, which enable to translate Fortran procedures directly
to C. In order to overcome all the difficulties related to the internal
structure of the library,  we interfaced all and just the
procedures and the variables exposed to the user. 
This module aims to foster interoperability of \NAME  with different
third party softwares as well as to support development of additional
API.

% \subsection{Dependent software}
% As a concrete example illustrating the interoperability of the
% software we here illustrate the case of EDIpy2, i.e. the Python API for
% \NAME and present an interface layer to Triqs (Toolbox
% for Reasearch In Quantum Systems).

\item{\bf EDIpy2.}
This is a simple Python module which provides Python API to the
\NAME Fortran library. This interface is built around the Python
support to C-types, which allows to import the dynamic C-binding
library generated upon building \NAME. The module contains a specific
class, whose methods mirrors through  duck-typing all the available
procedures of \NAME as well as it gives access to relevant shared
control variables.

\item{\bf EDIpack2Triqs.}
This is a thin interface layer from \NAME to Triqs,
built around the Python API of the \NAME library. The exact
diagonalization solver is encapsulated in a dedicated class,
containing the necessary methods to initialize and run a single
instance of the solver. The interface also includes a specific class
encompassing the effective discretized bath structure as well as their 
optimization methods.

\end{itemize}

% ##################################################################
% ##################################################################
% ##################################################################

@@

% ##################################################################
% ##################################################################
% ##################################################################

\section{Implementation}\label{SecEDIpack}
Here we present an overview of the implementation of the
different parts of the \NAME library.

@@

\subsection{Dynamical correlation functions}\label{sSecGF}

\subsection{Observables}\label{sSecObc}

\subsection{Reduced impurity density matrix}\label{sSecRDM}

\subsection{Bath parametrization}\label{sSecBath}

\subsection{Bath Optimization}\label{sSecFit}

\subsection{Input/Output}\label{sSecIO}

@@

% ##################################################################
% ##################################################################
% ##################################################################

% ##################################################################
% ##################################################################
% ##################################################################

@@

% ##################################################################
% ##################################################################
% ##################################################################
